\documentclass[]{article}
\usepackage[a4paper, total={6in, 8in}]{geometry}
\setlength\parindent{0pt}
\setlength{\parskip}{1em}
\thispagestyle{empty}

\begin{document}

{\Large BSSPC `19 P2 - Drawing}
\\\\
\textbf{\large Problem Statement}
\par
Drawing can be hard.
\par
Devin is trying to draw a picture on his computer, but he does not know how to use a graphics editor. 
\par
Help him out by making a program to turn his instructions into a picture!

\textbf{\large Input Specification}
\par
The first line will contain the integer $X$ and $Y$ ($1 \le X, Y \le 100$), with $X$ being the width of the canvas, and $Y$ being the height.
\par
The second line will contain the integer $N$ ($1 \le N < 10000$), which is the number of spots on the canvas he wants you to fill in.
\par
The following $N$ lines will contain the integers $x$ and $y$, and character $c$, where $x$ and $y$ is the location on the canvas Devin wants you to fill, and $c$ is the character to put at that spot.
\par
Note: The locations given ($x$ and $y$) start at 0, with (0, 0) being the top-left most corner. $x$ is the location along the width of the canvas, and $y$ is the location along the height of the canvas.

\textbf{\large Output Specification}
\par
Display the full canvas. Be sure to also output spaces where there is no character being filled.
\\\\
\textbf{\large Sample Input \#1}
\begin{verbatim}
5 1
3
0 0 a
2 0 r
4 0 t
\end{verbatim}

\textbf{\large Sample Output \#1}

\begin{verbatim}
a r t
\end{verbatim}

\textbf{\large Sample Input \#2}

\begin{verbatim}
8 3
15
3 0 _
1 1 _
2 1 [
3 1 _
4 1 ]
5 1 =
6 1 =
7 1 =
0 2 (
1 2 _
2 2 _
3 2 _
4 2 _
5 2 _
6 2 )
\end{verbatim}

\textbf{\large Sample Output \#2}

\begin{verbatim}
   _
 _[_]===
(_____) 
\end{verbatim}

\thispagestyle{empty}
\end{document}